---
title: 'Homework #2'
author: "Timothy Potter; tdpotter58"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



##R Commands
1. 
```{r}
cel <- c(-9, -23)
cel
```
2.
```{r}
vec200 <- rep(c(0,1),200)
vec200
```
3. 
```{r}
numPerfect <- 31
numPerfect
```


##Cars and Mileage
```{r}
library(ggplot2)
```

1.
The 3 most fuel-efficient cars are found by sorting the mpg dataset and then taking the top 3 values from that sorted set.
```{r}
mpg
hwy <- mpg[order(-mpg$hwy),]
top3 <- head(hwy, n = 3)
top3
```

2.
Just finding the sum of everytime compact appears and storing that in a variable
```{r}
numCompact = sum(mpg$class == "compact")
numCompact
```

3.
As the city mpg increases, so does the highway mpg. The reason so few points are visible is because most are repeated.
```{r}
qplot(hwy, cty, data = mpg)
```

4.
Cars do not seem to be more fuel efficient in 2008 than they were in 1999. In fact, it would appear that cars have gotten less efficient over time, as supported by the summary statistics.
```{r}
cars1999 <- mpg[mpg$year == 1999,]
cars1999 <- cars1999[order(-cars1999$hwy),]
cars1999
cars2008 <- mpg[mpg$year == 2008,]
cars2008 <- cars2008[order(-cars2008$hwy),]
cars2008

mean(cars1999$hwy)
mean(cars1999$cty)
mean(cars2008$hwy)
mean(cars2008$cty)
median(cars1999$hwy)
median(cars2008$hwy)
qplot(hwy, cty, data = cars1999)
qplot(hwy, cty, data = cars2008)
```